A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-13 article/04_Discussion.Rmd
introuction to the time series discussion

The following section contains a short evaluation of the time series in Figure \ref{development_burial_type} and \ref{development_burial_construction} in the light of the archaeological state of research for each region: \newline

@@

## Data quality

>>>>

One major question asked in this paper was, if openly available, bulk radiocarbon data does allow the reconstruction of main trends within the distribution of burial rites in Bronze Age Europe. This question can be answered with Yes. The narrative in section \ref{time-series-results} is surprisingly similar to the one presented by @hardingEuropeanSocietiesBronze2000a. The following paragraphs contain a short evaluation of the time series in Figure \ref{development_burial_type} and \ref{development_burial_construction} in the light of the archaeological state of research for each region. Despite the general success of this methodological apporach, unfortunately the amount and quality of data is not sufficient yet for a comprehensive picture. Please see the discussion of data quality in section \ref{data-quality-discussion}.

@@

## Data quality {#data-quality-discussion}
